STAT 450 Project: Real Estate

### 2020-03-24 src/2nd_draft.Rmd
added references

Refer to **Appendix** for forumlas of MSE and MSPE.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have a different objective function to optimize; they take a penalty in the sum of absolute values and sum of squared absolute values of weights respectively. These models have an interesting characteristic, that is, a weight is assigned to each feature. This might be relevant to our study as the mill rate can be affected by each feature to a different extent. Also, another advantage of these models is that MSPE is more stable as the variance of MSPE is reduced. For more detials about the two models, please refer to **Appendix**.

@@

After the 50 runs, a vector of MSEs and a vector of MSPEs for each model were therefore constructed successfully. Based on these vectors, side-by-side boxplots were used to show the mean and the spread of MSE and MSPE across all models respectively. For more details about cross-validation, please refer to **Appendix**.

@@

The p-values in Table 1 support that there is nonidentical distributions of mill rates across municipalities and tax classes.

@@

>>>>

Refer to **Reference** for forumlas of MSE and MSPE.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have a different objective function to optimize; they take a penalty in the sum of absolute values and sum of squared absolute values of weights respectively. These models have an interesting characteristic, that is, a weight is assigned to each feature. This might be relevant to our study as the mill rate can be affected by each feature to a different extent. Also, another advantage of these models is that MSPE is more stable as the variance of MSPE is reduced. For more detials about the two models, please refer to **Reference**.

@@

After the 50 runs, a vector of MSEs and a vector of MSPEs for each model were therefore constructed successfully. Based on these vectors, side-by-side boxplots were used to show the mean and the spread of MSE and MSPE across all models respectively. For more details about cross-validation, please refer to **Reference**.

@@

The p-values in Table 1 support that there is nonidentical distributions of mill rates across municipalities and tax classes.
Refer to **Reference** for more information on the Kruskal Wallis Test.

@@

Kruskal Wallis:
http://www.biostathandbook.com/kruskalwallis.html
